---
title: "What does the disaster say"
author: Yvonne Huang
subtitle: Emotional changes -- stampede in Itaewon
---

# Introduction

Disasters, such as storms, wildfires, and crowd stampede, occur and threaten human's physical and mental health. It is important to estimate social resilience because it represents population mental health. Therefore, understanding how people react and how their emotion changes toward disasters would be a crucial factor when analyzing social resilience. Twitter API allow users to access tweets within a week. Therefore, in this project, we collected tweets from three timeframes: before, during, and after disaster happened to analyze social resilience. To evaluate social resilience, Twitter data is used to produce social resilience index and analyze population emotion changes. Each tweet is spliced into words before sentiment analysis, and spaces, numbers, and special characters were removed. Emotion dictionaries provide sentiment emotion interval, such as positive, negative, and neutral, sentiment score, and emotions within each word. After data processing, tweets from each timeframe are summarize and provided a total sentiment score which represents the emotion level in each timeframe. The trend of sentiment emotion score changes is the symbol of social resilience. This project focused on analyzing people's emotional changes toward a crowd stampede incident in Itaewon, Seoul, South Korea on October 29, 2022. 

# Materials and methods
## Data
* Twitter API: TWitter allows every Twitter user to access tweets from the world within 1 week. Because accessing data requires user token and secret, this data is stored as .csv file to protect user's privacy. we collect data from Oct. 24 to Nov. 03. nearby Korea and Japan.
* City coordinates: maps database provide the coordinate of each city, it also includes the information of name and populations.
* Sentiment dictionaries:tidytext library provide the dictionaries with emotion information. bing, afinn, and nrc are used in this project.


Here are the libraries used in this project.
```{r, message=F, warning=F}
library(twitteR) 
library(rtweet)
library(dplyr)
library(tidytext)
library(textdata)
library(janeaustenr)
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(reshape2)
library(spData)
library(sf)
library(tidyverse)
library(maps)
library(wordcloud)
library(RColorBrewer)
library(wordcloud2)
library(tm)
knitr::opts_chunk$set(cache=TRUE)
```

## Download and clean all required data

Twitter data is already saved in "data" file, however, here is the example code demonstrate data downloading. To analyze sentiment changes, we collected tweets from three timeframes: before, during, and after disaster happened. We used the keyword "korea" to collect the tweets mention Korea.

```{r, message=F, warning=F, eval = FALSE}
consumer_key <- "XXX"
consumer_secret <-"XXX"
access_token <- "XXX"
access_secret <- "XXX" 
setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_secret)

# data accessing
loc = "35.7745, 123.3780, 200mi"

L0 <- searchTwitter("korea", n = 1000, lang = "en", geocode = loc,
                    since = "2022-10-24", until = "2022-10-29")
L1 <- searchTwitter("korea", n = 1000, lang = "en", geocode = loc,
                    since = "2022-10-29", until = "2022-10-31")
L2 <- searchTwitter("korea", n = 1000, lang = "en", geocode = loc,
                    since = "2022-11-01", until = "2022-11-03")

D0 <- twListToDF(L0)%>%
  mutate(timeline = "before")
D1 <- twListToDF(L1) %>%
  mutate(timeline = "during")
D2 <- twListToDF(L2) %>%
  mutate(timeline = "after")

data <- rbind(D0, D1, D2)
save_as_csv(data, "Twitter_disaster_1025_1103_K.csv")
```

A csv file (Twitter data) and Seoul location is read. Tweets locate nearby Seoul within 120 km are remained.
```{r, message=F, warning=F}
data <- read.csv("data/Twitter_disaster_1025_1103_K_1106.csv")
point <- st_as_sf(data, coords = c("longitude", "latitude"), crs = 4326)
data(world.cities)
seoul <- world.cities %>%
  filter(name == 'Seoul')%>%
  st_as_sf(coords = c("long", "lat"), crs = 4326)%>%
  st_buffer(dist = 120000)

data <- st_intersection(point, seoul)
```
 
Finally, we introduced sentiment dictionaries.
```{r, message=F, warning=F}
afinn = get_sentiments("afinn")
bing = get_sentiments("bing")
nrc = get_sentiments("nrc")
```


## Data processing

To under stand topic, keywords, and sentiment changes in tweets, tweets are sliced into words, and the frequency of each word using is calculated. Numbers, special characters, and spaces are removed from the analysis. Also, because all the tweets mention "korea", we removed the word "korea" from analysis.
```{r, message=F, warning=F}
steps <- c("before", "during", "after")

for (i in steps){
  data_temp <- data %>%
    filter(timeline == i)
  text_data <- data_temp$text
  docs_data <- Corpus(VectorSource(text_data))
  docs_data<- docs_data %>%
    tm_map(removeNumbers) %>%
    tm_map(removePunctuation) %>%
    tm_map(stripWhitespace)
  docs_data <- tm_map(docs_data, content_transformer(tolower))
  docs_data <- tm_map(docs_data, removeWords, stopwords("english"))
  dtm <- TermDocumentMatrix(docs_data) 
  matrix <- as.matrix(dtm) 
  words <- sort(rowSums(matrix),decreasing=TRUE) 
  df_data <- data.frame(word = names(words),freq=words) %>%
    filter(word != "korea" & word != "…" & word != "korea")
  assign(paste0("df", i), df_data)
  }
```


# Results
I am tired so I will write this part next time.

```{r, message=F, warning=F, fig.width=6, fig.height=3, fig.cap="Word cloud before stampede"}
wordcloud(words = dfbefore$word,
          freq = dfbefore$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))
```

```{r, message=F, warning=F, fig.width=6, fig.height=3, fig.cap="Word cloud during stampede"}
wordcloud(words = dfduring$word,
          freq = dfduring$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))
```

```{r, message=F, warning=F, fig.width=6, fig.height=3, fig.cap="Word cloud during stampede"}
wordcloud(words = dfafter$word,
          freq = dfafter$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))
```

I mean at least I have the plots.

```{r, message=F, warning=F, fig.width=6, fig.height=3, fig.cap="Positive and negative words used before stampede"}
dfbefore %>%
  inner_join(bing) %>%
  group_by(sentiment) %>%
  slice_max(freq, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, freq)) %>%
  ggplot(aes(freq, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```

```{r, message=F, warning=F, fig.width=6, fig.height=3, fig.cap="Positive and negative words used during stampede"}
dfduring %>%
  inner_join(bing) %>%
  group_by(sentiment) %>%
  slice_max(freq, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, freq)) %>%
  ggplot(aes(freq, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```

```{r, message=F, warning=F, fig.width=6, fig.height=3, fig.cap="Positive and negative words used after stampede"}
dfafter %>%
  inner_join(bing) %>%
  group_by(sentiment) %>%
  slice_max(freq, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, freq)) %>%
  ggplot(aes(freq, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```

OK we are here.

```{r, message=F, warning=F, fig.width=8, fig.height=6, fig.cap="Sentiment before stampede"}
dfbefore %>%
  inner_join(nrc) %>%
  mutate(temp = freq) %>%
  mutate(temp2 = sentiment) %>%
  pivot_wider(names_from = temp2, values_from = temp, values_fill = 0) %>% 
  mutate(score = positive - negative) %>%
  group_by(sentiment) %>%
  slice_max(order_by = freq, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, freq)) %>%
  ggplot(aes(freq, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```

```{r, message=F, warning=F, fig.width=8, fig.height=6, fig.cap="Sentiment before stampede"}
dfduring %>%
  inner_join(nrc) %>%
  mutate(temp = freq) %>%
  mutate(temp2 = sentiment) %>%
  pivot_wider(names_from = temp2, values_from = temp, values_fill = 0) %>% 
  mutate(score = positive - negative) %>%
  group_by(sentiment) %>%
  slice_max(order_by = freq, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, freq)) %>%
  ggplot(aes(freq, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```

```{r, message=F, warning=F, fig.width=8, fig.height=6, fig.cap="Sentiment before stampede"}
dfafter %>%
  inner_join(nrc) %>%
  mutate(temp = freq) %>%
  mutate(temp2 = sentiment) %>%
  pivot_wider(names_from = temp2, values_from = temp, values_fill = 0) %>% 
  mutate(score = positive - negative) %>%
  group_by(sentiment) %>%
  slice_max(order_by = freq, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, freq)) %>%
  ggplot(aes(freq, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```


Oh wait we have more?!!!

```{r, message=F, warning=F, fig.width=6, fig.height=3, fig.cap="Social resilience"}
dfbefore <- dfbefore %>%
  inner_join(afinn) %>%
  mutate(score = freq*value)
dfduring <- dfduring %>%
  inner_join(afinn) %>%
  mutate(score = freq*value)
dfafter <- dfafter %>%
  inner_join(afinn) %>%
  mutate(score = freq*value)

SCORE  <- c(sum(dfbefore$score), sum(dfduring$score), sum(dfafter$score))
timeframe <- c("-1", "0", "1")
names <- c("before", "during", "after")
trend <- data.frame(names,timeframe, SCORE)

ggplot(trend, aes(x= factor(names,level = c("before", "during", "after")), SCORE, group = 1))+
  geom_line(arrow = arrow())+
  geom_point()+
  xlab("timeline")+
  ylab("emotion score")+
  ggtitle("social resilience")+
  theme(plot.title = element_text(hjust = 0.5))
```

# Conclusions

[~200 words]

Clear summary adequately describing the results and putting them in context. Discussion of further questions and ways to continue investigation.

# References
* https://www.rdocumentation.org/packages/maps/versions/3.4.0/topics/world.cities
* http://www.sthda.com/english/wiki/text-mining-and-word-cloud-fundamentals-in-r-5-simple-steps-you-should-know
* https://www.tidytextmining.com/sentiment.html
* https://posit.co/blog/the-r-markdown-cheat-sheet/
